\textcolor{red}{Simple} connectome inference using partial correlation from imaging calcium signal

### 2014-06-17 article.tex
remove word
wording

The raw signal (original signal of Figure \ref{fig:filtered-signal}) is very noisy
due to light scattering artifacts that ordinarily affects the quality of the
recording (\cite{lichtman2011big}). A low-pass filter is first applied to
filter high frequency noises with one of the following filter designs
\begin{align}
% symmetrical median filter
x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
\label{eq:weighted-asymetric-median}.
\end{align}

A neuron spike lasts on average $1ms$ to $2ms$, while current optical
device have a time resolution of $20ms$. Considering the short delay for a
communication between neurons and slow decay of fluorescence signal, we
filter low frequencies through a high pass filter
\begin{align}
% an asymmetrical discrete derivative filter
x^{t,d}_{i} &\leftarrow x^{t}_i - x_{t-1}^i. \label{eq:high-pass-filter}
\end{align}

>>>>

The raw signal (original signal of Figure \ref{fig:filtered-signal}) is very noisy
due to light scattering artifacts that ordinarily affects the quality of the
recording (\cite{lichtman2011big}). A low-pass filter is first applied to
filter high frequency noises with one of the following designs
\begin{align}
% symmetrical median filter
x^t_i &\leftarrow x^{t-1}_i + x^{t}_i + x^{t+1}_i \label{eq:symetric-median}, \\
% asymmetrical weighted median
x^t_i &\leftarrow 0.4 x^{t-3}_i + 0.6 x^{t-2}_i + 0.8 x^{t-1}_i + x_{t}^i.
\label{eq:weighted-asymetric-median}.
\end{align}

A neuron spike lasts on average $1ms$ to $2ms$, while current optical
device have a time resolution of $20ms$. Considering the short delay for a
communication between neurons and the slow decay of fluorescence signal, we
filter low frequencies through a high pass filter
\begin{align}
% an asymmetrical discrete derivative filter
x^{t,d}_{i} &\leftarrow x^{t}_i - x_{t-1}^i. \label{eq:high-pass-filter}
\end{align}
